PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-12 docs/_tex/index.tex
fig updated
Bede's comments done

\subsection{Drone Data}\label{drone-data}

At each location, a DJI Matrice 200 quadcopter drone equipped with a
Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
million pixel reflectance photographs with ten spectral bands, from 444
nm (blue) to 840 nm (near infrared, NIR). To ensure consistent lighting
conditions across flight paths, the drone's trajectory was aligned to
maintain a solar azimuth angle of 90 degrees. An overlap of 70\% and
80\% (side and front respectively) between each image was set for each
flight. A downwelling light sensor (DLS2) was used to acquire irradiance
data concomitantly with the camera measurements. Raw data were
calibrated in reflectance using a calibration panel reflective at
\textasciitilde50\% provided by the manufacturer. A
structure-from-motion photogrammetry software (Agisoft Metashape) was
used to process images to obtain multispectral orthomosaics of each
flight. The workflow for orthomosaicking was the same for every flight.
First, tying key points were detected inside of each image and between
overlapping images in order to obtain a sparse point cloud. This cloud
was cleaned using reprojection accuracy metric in order to remove noisy
points. A dense point cloud was then produced using a structure from
motion algorithm. A surface interpolation of this dense point cloud was
made to obtain a digital surface model (DSM), used to reconstruct the
multispectral ortho-image. Across all sites, flights were made at two
different altitudes : 12 m or/and 120 m. Low altitude drone flights
produce ortho-images with a very high spatial resolution (8 mm per
pixel), making it efficient to visually distinguish between the various
types of vegetation. High altitude fights on the other hand allow to
cover large areas and produced images with a pixel size of 80 mm
(Table~\ref{tbl-flights}).

@@

@@

\subsection{Intertidal vegetation
mapping}\label{intertidal-vegetation-mapping}

@@

@@

@@

\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
both low-altitude and high-altitude flights over a common area. The
black dashed line represents a 1 to 1 relationship. Left (A) plots raw
data and right (B) plots standardised data.}

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enabled precise
selection of pure pixels representing the classes used in the neural
network model. This methodology implies a consistency between the
reflectance of both altitude. Figure~\ref{fig-CompareRef} depicts the
relationship between reflectance from a low-altitude flight and a
high-altitude flight conducted over the same area. Overall there was a
good agreement between the two altitudes. There was however a slight
underestimation for raw reflectance values in the high-altitude flight,
particularly for higher values (Figure~\ref{fig-CompareRef} A). Since
both flights were conducted over vegetation areas, the highest
reflectance values correspond to the infrared part of the spectrum.

The disparity in infrared reflectance may stem from temporal differences
between the flights, possibly resulting in a slightly drier intertidal
area and consequently higher infrared reflectance. This disparity poses
an issue for the methodology followed in the present study, relying
solely on one flight height for training. To address this issue, we
employed min/max standardized reflectance spectra as predictors for the
model (Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allowed
us to eliminate the slight reflectance difference between the flights
(Figure~\ref{fig-CompareRef} B) and to focus on the shape of the spectra
in the visible part of the electromagnetic spectra, where different
pigmentation are associated to taxonomic dignostic features. This was a
key feature in building a model that could reliably predict vegetation
across geographical sites and seasons. It enabled consistent prediction
of vegetation classes across variations in biomass and variability in
light conditions \citetext{\citealp[ ]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

>>>>

\subsubsection{Drone acquisition}\label{drone-acquisition}

At each location, a DJI Matrice 200 quadcopter drone equipped with a
Micasense RedEdge Dual MX multispectral camera was flown to take 1.2
million pixel reflectance photographs with ten spectral bands, from 444
nm (blue) to 840 nm (near infrared, NIR). To ensure consistent lighting
conditions across flight paths, the drone's trajectory was aligned to
maintain a solar azimuth angle of 90 degrees. An overlap of 70\% and
80\% (side and front respectively) between each image was set for each
flight. A downwelling light sensor (DLS2) was used to acquire irradiance
data concomitantly with the camera measurements. Raw data were
calibrated in reflectance using a calibration panel reflective at
\textasciitilde50\% provided by the manufacturer. Across all sites,
flights were made at two different altitudes : 12 m or/and 120 m.
(Table~\ref{tbl-flights}).

@@

\subsubsection{Ground Control Points}\label{ground-control-points}

@@

\subsection{Drone Processing}\label{drone-processing}

A structure-from-motion photogrammetry software (Agisoft Metashape) was
used to process images to obtain multispectral orthomosaics of each
flight. The workflow for orthomosaicking was the same for every flight.
First, tying key points were detected inside of each image and between
overlapping images in order to obtain a sparse point cloud. This cloud
was cleaned using reprojection accuracy metric in order to remove noisy
points. A dense point cloud was then produced using a structure from
motion algorithm. A surface interpolation of this dense point cloud was
made to obtain a digital surface model (DSM), used to reconstruct the
multispectral ortho-image. Low altitude drone flights produce
ortho-images with a very high spatial resolution (8 mm per pixel),
making it efficient to visually distinguish between the various types of
vegetation. High altitude fights on the other hand allow to cover large
areas and produced images with a pixel size of 80 mm
(Table~\ref{tbl-flights}).

\subsection{General Workflow}\label{general-workflow}

@@

Variable Importance Plots (VIP) serve as a method to identify which
predictors are important for predicting a specific class. This is
achieved by repeatedly predicting the same dataset while shuffling one
predictor at a time. The benchmark score obtained after each iteration
is then compared to the benchmark score obtained without shuffling any
variables. The greater the difference between these two benchmark
values, the more important the variable is for the model
\citep{WEI2015399}.

@@

\subsubsection{Reflectance comparison between the two different
altitudes}\label{reflectance-comparison-between-the-two-different-altitudes}

\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
both low-altitude and high-altitude flights over a common area. The
black dashed line represents a 1 to 1 relationship. Left (A) plots raw
data and right (B) plots standardized data (Equation~\ref{eq-std}).}

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enabled precise
selection of pure pixels representing the classes used in the neural
network model. This methodology implies a consistency between the
reflectance of both altitude. Figure~\ref{fig-CompareRef} depicts the
relationship between reflectance from a low-altitude flight and a
high-altitude flight conducted over the same area. Overall there was a
good agreement between the two altitudes. There was however a slight
underestimation for raw reflectance values in the high-altitude flight,
particularly for higher values (Figure~\ref{fig-CompareRef} A). Since
both flights were conducted over vegetation areas, the highest
reflectance values correspond to the infrared part of the spectrum. This
different is not present anymore when reflectance values of both flights
have been standardized (Equation~\ref{eq-std} ;
Figure~\ref{fig-CompareRef} B).

\subsubsection{Neural network classification
validation}\label{neural-network-classification-validation}

@@

While comparing the reflectance of both altitudes (12 m and 120 m), it
was observed Figure~\ref{fig-CompareRef} that there is an
underestimation of the infrared part of the spectra in the high-altitude
dataset. The disparity in infrared reflectance may stem from temporal
differences between the flights, possibly resulting in a slightly drier
intertidal area and consequently higher infrared reflectance. This
disparity poses an issue for the methodology followed in the present
study, relying solely on one flight height for training. To address this
issue, we employed min/max standardized reflectance spectra as
predictors for the model (Equation~\ref{eq-std} ; \citep{Cao2017}). This
approach allowed us to eliminate the slight reflectance difference
between the flights (Figure~\ref{fig-CompareRef} B) and to focus on the
shape of the spectra in the visible part of the electromagnetic spectra,
where different pigmentation are associated to taxonomic dignostic
features. This was a key feature in building a model that could reliably
predict vegetation across geographical sites and seasons. It enabled
consistent prediction of vegetation classes across variations in biomass
and variability in light conditions \citetext{\citealp[
]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

### 2024-03-12 index.qmd
Bede's comments done

Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class. This is achieved by repeatedly predicting the same dataset while shuffling one predictor at a time. The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables. The greater the difference between these two benchmark values, the more important the variable is for the model (@WEI2015399).

@@

@@

```{r Reflectance_Validation 2 height}
#| cache: true
#| echo: false
#| eval: false
#| warning: false

```{r RefComapare}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The black dashed line represents a 1 to 1 relationship. Left (A) plots raw data and right (B) plots standardised data. 
#| label: fig-CompareRef
#| fig-width: 10
#| fig-height: 5
#| out-width: "100%"

In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude. @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. Overall there was a good agreement between the two altitudes. There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher values (@fig-CompareRef A). Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.

The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]). This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features. This was a key feature in building a model that could reliably predict vegetation across geographical sites and seasons. It enabled consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].

>>>>

Variable Importance Plots (VIP) serve as a method to identify which predictors are important for predicting a specific class. This is achieved by repeatedly predicting the same dataset while shuffling one predictor at a time. The benchmark score obtained after each iteration is then compared to the benchmark score obtained without shuffling any variables. The greater the difference between these two benchmark values, the more important the variable is for the model [@WEI2015399].

@@

### Reflectance comparison between the two different altitudes
```{r Reflectance_Validation 2 height}
#| cache: true
#| echo: false
#| eval: false
#| warning: false

```{r RefComapare}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The black dashed line represents a 1 to 1 relationship. Left (A) plots raw data and right (B) plots standardized data (@eq-std). 
#| label: fig-CompareRef
#| fig-width: 10
#| fig-height: 5
#| out-width: "100%"

In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enabled precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude. @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. Overall there was a good agreement between the two altitudes. There was however a slight underestimation for raw reflectance values in the high-altitude flight, particularly for higher values (@fig-CompareRef A). Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum. This different is not present anymore when reflectance values of both flights have been standardized (@eq-std ; @fig-CompareRef B).

### Neural network classification validation

@@

While comparing the reflectance of both altitudes (12 m and 120 m), it was observed @fig-CompareRef that there is an underestimation of the infrared part of the spectra in the high-altitude dataset. The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]). This approach allowed us to eliminate the slight reflectance difference between the flights (@fig-CompareRef B) and to focus on the shape of the spectra in the visible part of the electromagnetic spectra, where different pigmentation are associated to taxonomic dignostic features. This was a key feature in building a model that could reliably predict vegetation across geographical sites and seasons. It enabled consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].
